Modal Abstractions for Virtualizing Memory Addresses

### 2024-07-03 examples.tex
+

$\specline{}$
callq  c0 <pte_get_next_table_succ>
;;save the physical next table address in rax
mov    rax,-0x20[rbp]
$\specline{}$
;;pte_t *pdp_entry = &pdp[PDPEX(va)];
;;pte_t *pd = pte_get_next_table_succ(pdp_entry);
$\specline{}$
...
;;pte_t *pd_entry = &pd[PDEX(va)];
;;pte_t *pt = pte_get_next_table_succ(pd_entry);
 $\specline{}$
;;return &pt[PTEX(va)];
...
;; clean up the stack 
\end{lstlisting}
\vspace{-1em}
\caption{Walking page-table directory via calls to \textsf{pte\_get\_next\_table} in Figure \ref{fig:calltopteinitialize}}
\label{walkpgdir}
\end{figure}
%\begin{figure}\footnotesize
%\begin{lstlisting}[mathescape]
%;;if (!entry->present) {
%  ...
%
%;;}
%...
%$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi,m)  \ast \texttt{rbp-8} \mapsto_{\textsf{v}} \textsf{entry} \ast \texttt{r8}  \mapsto_{\textsf{r}} \textsf{\_} \ast \texttt{rdi}  \mapsto_{\textsf{r}} \textsf{\_} \ast \sumpv\paddr\qfrac\true  \sumapaces\rtv\delta  }_{\rtv}$ 
%mov    rax,-0x18[rbp]
 % 
%;;uintptr_t next_virt_addr = (uintptr_t) P2V(next_phys_addr);
%mov    -0x18[rbp],rax
%movabs 0x0,rcx            187: R_X86_64_64	KERN_BASE
%add    rcx,rax
%mov    rax,-0x20[rbp]
%\end{lstlisting}
%\vspace{-1em}
%\caption{Converting a physical address, whose exsitence is made certain, of a PTE to a virtual address (w/o instruction pointer or flag updates). $R$ abbreviates the resources
%associated with \paddr\ by $\Xi$ in Figure \ref{fig:peraspaceinvariant_with_p2v_extension}.}
%\label{fig:p2v}
%\end{figure}

>>>>

$\specline{P_0 }_{\rtv}$
callq  c0 <pte_get_next_table_succ>
;;save the physical next table address in rax
$\specline{P_1 \ast \texttt{pdp} \mapsto_{\textsf{vpte,qfracn}} \textsf{pdppaddr \_} }_{\rtv}$
;;pte_t *pdp_entry = &pdp[PDPEX(va)];
;;pte_t *pd = pte_get_next_table_succ(pdp_entry);
$\specline{P_2 \ast \texttt{pdp} \mapsto_{\textsf{vpte,qfracn}} \textsf{pdppaddr w64\_zero} \ast \texttt{pd} \mapsto_{\textsf{vpte,qfracn}} \textsf{pdpaddr \_} }_{\rtv}$
;;pte_t *pd_entry = &pd[PDEX(va)];
;;pte_t *pt = pte_get_next_table_succ(pd_entry);
$\specline{P_3 \ast \texttt{pdp} \mapsto_{\textsf{vpte,qfracn}} \textsf{pdppaddr w64\_zero} \ast \texttt{pd} \mapsto_{\textsf{vpte,qfracn}} \textsf{pdpaddr \_} \ast \texttt{pt} \mapsto_{\textsf{vpte,qfracn}} \textsf{ptpaddr \_} }_{\rtv}$
;;access and return L1 entry
;;return &pt[PTEX(va)];
;; clean up the stack 
\caption{Walking page-table directory via calls to \textsf{pte\_get\_next\_table} in Figure \ref{fig:calltopteinitialize}}
\label{walkpgdir}
%\begin{figure}\footnotesize
%\begin{lstlisting}[mathescape]
%;;if (!entry->present) {
%  ...
%;;}
%...
%$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi,m)  \ast \texttt{rbp-8} \mapsto_{\textsf{v}} \textsf{entry} \ast \texttt{r8}  \mapsto_{\textsf{r}} \textsf{\_} \ast \texttt{rdi}  \mapsto_{\textsf{r}} \textsf{\_} \ast \sumpv\paddr\qfrac\true  \sumapaces\rtv\delta  }_{\rtv}$ 
%mov    rax,-0x18[rbp]
%;;uintptr_t next_virt_addr = (uintptr_t) P2V(next_phys_addr);
%mov    -0x18[rbp],rax
%movabs 0x0,rcx            187: R_X86_64_64	KERN_BASE
%add    rcx,rax
%mov    rax,-0x20[rbp]
%\end{lstlisting}
%\vspace{-1em}
%\caption{Converting a physical address, whose exsitence is made certain, of a PTE to a virtual address (w/o instruction pointer or flag updates). $R$ abbreviates the resources
%associated with \paddr\ by $\Xi$ in Figure \ref{fig:peraspaceinvariant_with_p2v_extension}.}
%\label{fig:p2v}
%\end{figure}
